Halo alignments with large scale tidal and velocity fields

### 2013-05-20 paper/main.tex
more text on the historical summary

\citep{Faltenbacher2009} %galaxy alignments with mocks
\citep{Paz2008} %angular momentum alignments
\citep{Platen2008} %alignment in voids
\citep{Lee2007}%Obs. spin alignment

@@

@@

\item 
\citep{AragonCalvo2007} %Spin alignment
The method is the Multi-scale Morphology Filter which is based on the
Hessian matrix of the density field, where the density field is
computed from the particle distribution using a Delaunay tesselation
field estimatior (DTFE), which is self-adaptive. This allows them to
identify clusters, filaments and walls.

@@

\item
\citep{Brunino2007}

>>>>

@@

\citep{Faltenbacher2009} %galaxy alignments with mocks

The tidal connection between voids in simulations \citep{Platen2008},
the alignment of observed galaxies with the inferred tidal
field\citep{Lee2007,Jones2010}

@@

\item
\citep{Paz2008} %angular momentum alignments
Nelson? Puedes hacer un resumen?

\item 
\citep{AragonCalvo2007} %angular momentum alignment
The method is the Multi-scale Morphology Filter which is based on the
Hessian matrix of the density field, where the density field is
computed from the particle distribution using a Delaunay tesselation
field estimatior (DTFE), which is self-adaptive. This allows them to
identify clusters, filaments and walls.

@@

\item
\citep{Brunino2007}
Uses a DM only N-body simulation (the Millennium Run) to study the
shape and angular momentum alignment with respect to large
cosmological voids.

The voids are found with a spherical void finder. This algorithm first
looks for potential void centers in the underdense regions of the
simulation. These positions define the centers of spheres that are
empty of halos above a given mass threshold. Only voids with radius
larger than $10$\hMpc were considered for further analysis.

Halos were identified by linking particles with density exceeding 900
times the background density in order to keep the analysis of shape
and angular momentum on the core of the halo. Only halos with masses
in the range $8.6\times 10^{11}\hMsun < M_{\mathrm h}< 8.6\times
10^{12}\hMsun$ were included analized to measure their angular
momentum and the inertia tensor, both in a non-normalized way.

For the purpose of measuring alignments a second cut is imposed
whereby only halos within a shell of radius $R_{\mathrm void}<r<1.05R_{\mathrm
void}$. The alignment is then measured between the vector connecting
the center of the void to the halo in question and the vector of
interest.

The results show that there is a strong alignment of halo shape in
such a way that the major axis is parallel to the shell surrounding
the void. In the case of angular momentum there is not a significant
signal for alignment.
